---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# RECOMBINE

## Overview

RECOMBINE (REcurrent COmposite Markers for Biological Identities with Neighborhood Enrichment) is a computational framework for unbiased selection of discriminant markers that hierarchically distinguish cells and extraction of recurrent composite markers (RCMs) that characterize cell types and states with high granularity.

RECOMBINE consists of two steps. The first step employs sparse hierarchical clustering with spike-and-slab lasso (SHC-SSL) to select features that discriminate hierarchical cell subpopulations from high dimensional data such as scRNA-seq. The second step employs neighborhood recurrence test to extract RCMs at the cell and subpopulation levels.

## Installation

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("korkutlab/recombine")
```

## Tutorials

Tutorial 1: RECOMBINE identifies recurrent composite markers for common and rare cell subpopulations of mouse intestinal organoids (https://github.com/korkutlab/recombine/blob/main/inst/tutorials/intestine_scRNA/intestine_scRNA.md)

Tutorial 2: RECOBMINE selects unbiased marker panel from scRNA-seq data for targeted spatial transcriptomics (https://github.com/korkutlab/recombine/blob/main/inst/tutorials/mvc_scRNA_spatial/mvc_scRNA_spatial.md)

Tutorial 3: RECOMBINE SHC-SSL performs accurate feature selection coupled with hierarchical clustering (https://github.com/korkutlab/recombine/blob/main/inst/tutorials/sim/sim.md)

<!-- ## Citation -->
<!-- Li X. and Korkut A. (2023) Recurrent composite markers of cell types and states.  -->
